\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-06-14 metatheory.tex
Save.
Save. Working on the example
light edits

Though phrased in Latex, we are following \citep{kaposi2017type} to use as our meta-logic a type theoretical framework (like Agda) , 
together with \textit{Quotient Inductive Inductive Type} (QIIT). Each judgement will actually be represented by a QIIT type, which are mutual-recursively defined together. Quotient is used to represent judgemental(definitional) equality, thanks to which we can have a concise representation. This way, for all four kinds of judgement we are using, there are always equality among these data. Doing so, we can omit some obvious equality judgement. Most of the reasoning can be formulated using the \textit{algebra} of QIIT (mapping out function from this quotient data-type).

@@

\newcommand{\denotes}[1]{{\llbracket {#1} \rrbracket}}
\newcommand{\goodCtx}[2]{{ {#1} \ ok }}
\newcommand{\goodType}[3]{{ {#1} \vdash {#2} }}
\newcommand{\goodTerm}[3]{{ {#1} \vdash {#2} : {#3} }}
\newcommand{\goodSub}[3]{{ {#1} \vdash {#2} : {#3} }}
\newcommand{\goodSig}[3]{{ {#1} \vdash {#2} \ \  Sig^{#3} }}
\newcommand{\goodWSig}[3]{{ {#1} \vdash {#2} \ \ WSig^{#3} }}
\newcommand{\goodSeal}[4]{{ {#1} \vdash {#2} : {#3} \  |\  {#4} }}
\newcommand{\goodInh}[4]{{ {#1} \vdash {#2} : {#3} \twoheadrightarrow {#4}}}
\newcommand{\nat}{\mathbf{N}}

\newcommand{\cU}{{\mathcal{U}}}
\newcommand{\cB}{{\mathbb{B}}}
\newcommand{\cL}{{\mathcal{L}}}
\newcommand{\bW}{{\mathbb{W}}}

@@

\subsection{Proof Relevant Logical Relation for Canonicity}
We follow \citep{sterling2019algebraic,coquand2018canonicity} to construct the canonicity model.

>>>>

Though phrased in Latex, we are following \citep{kaposi2017type} to use as our meta-logic a type theoretical framework (like Agda) , 
together with \textit{Quotient Inductive Inductive Type} (QIIT). Each
judgement will actually be represented by a QIIT type, which are
mutually recursively defined together. Quotient is used to represent
judgemental(definitional) equality, thanks to which we can have a
concise representation. This way, for all four kinds of judgement we are
using, there are always equality among these data. Doing so, we can omit
some obvious equality judgement. Most of the reasoning can be formulated
using the \textit{algebra} of QIIT (mapping out function from this
quotient data-type).

@@

\newcommand{\denotes}[1]{{\llbracket {#1} \rrbracket}}
\newcommand{\denotesS}[1]{{{\llbracket {#1} \rrbracket}_S}}
\newcommand{\goodCtx}[2]{{ {#1} \ \vdash }}
\newcommand{\goodType}[3]{{ {#1} \vdash {#2} }}
\newcommand{\goodTerm}[3]{{ {#1} \vdash {#2} : {#3} }}
\newcommand{\goodSub}[3]{{ {#1} \vdash {#2} : {#3} }}
\newcommand{\goodSig}[3]{{ {#1} \vdash {#2} \ \  Sig^{#3} }}
\newcommand{\goodWSig}[3]{{ {#1} \vdash {#2} \ \ WSig^{#3} }}
\newcommand{\goodSeal}[4]{{ {#1} \vdash {#2} : {#3} \  |\  {#4} }}
\newcommand{\goodInh}[4]{{ {#1} \vdash {#2} : {#3} \twoheadrightarrow {#4}}}
\newcommand{\nat}{\mathbf{N}}

\newcommand{\cU}{{\mathcal{U}}}
\newcommand{\cB}{{\mathbb{B}}}
\newcommand{\cL}{{\mathcal{L}}}
\newcommand{\cC}{{\mathcal{C}}}
\newcommand{\cCt}{{\mathcal{C}_t}}
\newcommand{\bW}{{\mathbb{W}}}

@@

\subsection{Proof Relevant Logical Relation for Canonicity}
\input{canonicitymodel.tex}

### 2022-06-14 syntax.tex
Save.
light edits

Firstly, there are four standard kinds of judgement in MLTT, well-typed context $\goodCtx{\Gamma}{l}$, well-typed type $\goodType{\Gamma}{T}{l}$, well-typed term $\goodTerm{\Gamma}{t}{T}$ and well-typed substitution $\goodSub{\Gamma}{\gamma}{\Delta}$. We are following \citep{kaposi2019gluing} but we will omit the universe level attached to the judgement here, to make it more readable. After these, we will have four new kinds of judgement to model our linkage.

Because we formalize our language as a deep embedding in a type theory with QIIT types, every judgement is a (dependent) QIIT \textit{type} and all judgement derivations are well-typed QIIT terms (otherwise how can they be encoded in Agda?)
%\YZ{What's the distinction of judgments vs. sequents?}.\EDJreply{I am not sure about the correct terminology here. Here I want to say "even underivable judgement has to be well-typed". That's the main reason I spell out the fake Agda code there. I actually want the reader to have intrinsic-typed syntax in mind all the time (like read conventional math but acknowledge we are manipulating Agda)}\EDJreply{I rephrase that so there won't be confusion for the future readers. Please check}
Latex-wise, we spell out these \textit{well-formed-ness rule} of type judgements and their Agda counterpart to make things more accessible. Of course, a well-formed judgement is not necessarily derivable, just like a well-typed QIIT type is not necessarily inhabited.

>>>>

Firstly, there are four standard judgement forms in MLTT,
well-typed contexts $\goodCtx{\Gamma}{l}$, well-typed types
$\goodType{\Gamma}{T}{l}$, well-typed terms $\goodTerm{\Gamma}{t}{T}$, and
well-typed substitutions $\goodSub{\Gamma}{\gamma}{\Delta}$. Our presentation
follows the style of \citep{kaposi2019gluing}, but for readability we
omit universe levels attached to judgements.
After these,
we will have four new kinds of judgement to model our linkage.

Because we formalize our language as a deep embedding in a type theory with QIIT types, every judgement is a (dependent) QIIT \textit{type} and all judgement derivations are well-typed QIIT terms (otherwise how can they be encoded in Agda?)
%\YZ{What's the distinction of judgments vs. sequents?}.\EDJreply{I am not sure about the correct terminology here. Here I want to say "even underivable judgement has to be well-typed". That's the main reason I spell out the fake Agda code there. I actually want the reader to have intrinsic-typed syntax in mind all the time (like read conventional math but acknowledge we are manipulating Agda)}\EDJreply{I rephrase that so there won't be confusion for the future readers. Please check}
Latex-wise, we spell out these \textit{well-formedness rule} of type
judgements and their Agda counterpart to make things more accessible. Of
course, a well-formed judgement is not necessarily derivable, just like
a well-typed QIIT type is not necessarily inhabited.
